---
title: "R Notebook"
output: html_notebook
---
```{r}
library(ggplot2)
library(stringr)
library(dplyr)
library(patchwork)
library(tidyr)
library(matrixStats)
library(tidyverse)

```

```{r input}
mhcii_asyn_bfactor <- read_csv("~/mhcii_data/nativecontacts_pdb/mhcii_asyn_bfactor.csv")
tcr_asyn_bfactor <- read_csv("~/mhcii_data/nativecontacts_pdb/tcr_asyn_bfactor.csv")
tcr_mhcii_bfactor <- read_csv("~/mhcii_data/nativecontacts_pdb/tcr_mhcii_bfactor.csv")
```

```{r data manipulation}
#summary(tcr_mhcii)
#mhcii_asyn_avgtrials <- mhcii_asyn_bfactor %>%
#  group_by(resseq, Protein, Chain) %>%
#  summarise(fac_mean = mean(tempfactor), fac_sd = sd(tempfactor))

tcr_mhcii_avgtrials <- tcr_mhcii_bfactor %>%
  group_by(resseq, DNEAY, Chain, Protein) %>%
  summarise(fac_mean = mean(tempfactor), fac_sd = sd(tempfactor))

tcr_asyn_avgtrials <- tcr_asyn_bfactor %>%
  group_by(resseq, DNEAY, Chain, Protein) %>%
  summarise(fac_mean = mean(tempfactor), fac_sd = sd(tempfactor))
```
```{r tcr_asyn plot}
tcr_asyn_avgtrials %>%
  filter(DNEAY==TRUE)%>%
  ggplot()+
  geom_point(aes(x=resseq, y=fac_mean, color = Chain))+
  facet_grid(, vars(Protein))+
  geom_errorbar(aes(x=resseq, ymin=fac_mean-fac_sd, ymax=fac_mean+fac_sd, color = Chain), width=.1,
                 position=position_dodge(0.05))+
  theme(panel.grid=element_blank(), legend.position="bottom", legend.box = "horizontal")+
  labs(x = "Residue Number", y = "Relative Contact Strength")#+
  #geom_text(aes(x=resseq, y=fac_mean, color = Chain, label=resseq), hjust=0, vjust=0)

tcr_asyn_avgtrials %>%
  filter(DNEAY==FALSE)%>%
  ggplot()+
  geom_point(aes(x=resseq, y=fac_mean, color = Chain, label=resseq))+
  facet_grid(, vars(Protein))+
  geom_errorbar(aes(x=resseq, ymin=fac_mean-fac_sd, ymax=fac_mean+fac_sd, color = Chain), width=.1,
                 position=position_dodge(0.05))+
  theme(panel.grid=element_blank(), legend.position="bottom", legend.box = "horizontal")+
  labs(x = "Residue Number", y = "Relative Contact Strength")#+
  #geom_text(aes(x=resseq, y=fac_mean, color = Chain, label=resseq), hjust=0, vjust=0)
```

```{r tcr_mhcii plot}
#[contactpdb <file>] Write PDB with B-factor column containing relative contact strength for native contacts (strongest is 100.0).

tcr_mhcii_avgtrials %>%
  filter(DNEAY==TRUE)%>%
  ggplot()+
  geom_point(aes(x=resseq, y=fac_mean, color = Chain))+
  facet_grid(, vars(Protein))+
  geom_errorbar(aes(x=resseq, ymin=fac_mean-fac_sd, ymax=fac_mean+fac_sd, color = Chain), width=.1,
                 position=position_dodge(0.05))+
  theme(panel.grid=element_blank(), legend.position="bottom", legend.box = "horizontal")+
  labs(x = "Residue Number", y = "Relative Contact Strength")#+
  #geom_text(aes(x=resseq, y=fac_mean, color = Chain, label=resseq), hjust=0, vjust=0)

tcr_mhcii_avgtrials %>%
  filter(DNEAY==FALSE)%>%
  ggplot()+
  geom_point(aes(x=resseq, y=fac_mean, color = Chain, label=resseq))+
  facet_grid(, vars(Protein))+
  geom_errorbar(aes(x=resseq, ymin=fac_mean-fac_sd, ymax=fac_mean+fac_sd, color = Chain), width=.1,
                 position=position_dodge(0.05))+
  theme(panel.grid=element_blank(), legend.position="bottom", legend.box = "horizontal")+
  labs(x = "Residue Number", y = "Relative Contact Strength")#+
  #geom_text(aes(x=resseq, y=fac_mean, color = Chain, label=resseq), hjust=0, vjust=0)
```
```{r}
ggplot(data = tcr_mhcii, aes(MHCII_res))+
  geom_histogram(stat="count")
ggplot(data = tcr_mhcii, aes(TCR_res))+
  geom_histogram(stat="count")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

