---
title: "R Notebook"
output: html_notebook
---
```{r}
library(dplyr)
```

```{r input}
tcr_chainA = read.table("nativecontacts_tcr_chainA.dat", comment = "#", col.names= c("Num", "Molecules","Frames","Frac","Avg", "Stdev", "Protein", "Trial")) %>%
  mutate(Bonds=Molecules)%>%
  separate(Molecules, c("TCR", "MHCII"), sep = "_") %>%
  separate(TCR, c("TCR_res", "TCR_atom"), sep = "@")%>%
  separate(MHCII, c("MHCII_res", "MHCII_atom"), sep = "@")
```

```{r data manipulation}
#summary(tcr_chainA)
sumbyres <- tcr_chainA %>%
  group_by(TCR_res,MHCII_res, Protein) %>%
  #select(TCR_res,MHCII_res, Frac, Avg) %>%
  summarise(Frac_mean = mean(Frac), Frac_sd = sd(Frac), Dist_mean = mean(Avg)) %>%
  unite("Bonds", TCR_res:MHCII_res)

sumbyres <- sumbyres %>%
  group_by(Bonds) %>%
  mutate(n = n()) %>%
  arrange(desc(Frac_mean))%>%
  filter(n > 4) %>%
  slice(1:100)
```

```{r plot_Frac}
sumbyres %>%
  ggplot()+
  geom_point(aes(x=Bonds, y=Frac_mean))

sumbyres %>%
  ggplot()+
  geom_point(aes(x=Bonds, y=Frac_mean))+
  facet_grid(vars(Protein))
```
```{r}
ggplot(data = tcr_chainA, aes(MHCII_res))+
  geom_histogram(stat="count")
ggplot(data = tcr_chainA, aes(TCR_res))+
  geom_histogram(stat="count")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

